%-----------PROJECTS-----------%
\section{\faTasks \textbf{ Projects}}
\resumeSubHeadingListStart
    
    \resumeProjectHeading
    {\textbf{Greater Dalton 2050 Metropolitan Transportation Plan, GA} $|$ \emph{Metro Analytics}}{2024}
    \resumeItemListStart
        \resumeItem{For the Greater Dalton 2050 Metropolitan Transportation Plan, base year and future year socioeconomic data were prepared for travel demand model calibration. Existing data at the Traffic Analysis Zone (TAZ) level were compiled from the US Decennial Census, American Community Survey, and Longitudinal Employer-Household Dynamics data, then calibrated using satellite imagery and local sources. Projections were developed based on state control totals and best practices. The result was a set of socioeconomic data, including population, household, and employment characteristics, to be used in calibrating trip generation and travel demand at each TAZ.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Bowling Green – Warren County 2050 Metropolitan Transportation Plan, KY} $|$ \emph{Metro Analytics}}{2024}
    \resumeItemListStart
        \resumeItem{For the Bowling Green-Warren County 2050 Metropolitan Transportation Plan, the regional travel demand model was calibrated using existing traffic data and modified for future no-build, fiscally constrained, and unconstrained funding scenarios. Model outputs were summarized, maps of projected traffic volumes and congestion were generated, and technical memoranda with scenario analysis and statistics were produced to support decision-making in the MTP development.}
    \resumeItemListEnd
    
    \resumeProjectHeading
    {\textbf{\href{https://tmacog.org/transportation/freight-plan}{TMACOG Freight Profile, OH}} $|$ \emph{Metro Analytics}}{2024}
    \resumeItemListStart
        \resumeItem{For the TMACOG Freight Profile project, support was provided to the Toledo Metropolitan Area Council of Governments in updating its regional freight plan. The role involved assisting in the preparation of the freight profile, needs assessment, and recommendations. Key data were collected, including transportation asset conditions (bridges and pavement), safety data (traffic crashes), and traffic data (daily and truck volumes, congestion). GIS maps were created to analyze this information. The result was a comprehensive freight profile that assessed existing infrastructure, identified gaps, and recommended strategies for improving freight transportation in the region.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Valdosta-Lowndes MPO 2050 Metropolitan Transportation Plan, GA} $|$ \emph{Metro Analytics}}{2024}
    \resumeItemListStart
        \resumeItem{For the Valdosta-Lowndes MPO 2050 Metropolitan Transportation Plan, support was provided as a planner and analyst for the Metropolitan Transportation planning process. Socioeconomic data at the Traffic Analysis Zone (TAZ) level for both base and future years were prepared, and assistance was provided in GIS mapping of existing transportation assets, needs assessment, and project identification. The result was the preparation of TAZ-level socioeconomic data, GIS maps for the existing conditions report, and contributions to the needs assessment and final documentation.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{\href{https://apps.trb.org/cmsfeed/TRBNetProjectDisplay.asp?ProjectID=4957}{NCHRP 08-146: Integrating Resiliency into Transportation System Operations}} $|$ \emph{Metro Analytics}}{2024}
    \resumeItemListStart
        \resumeItem{The project, sponsored by the National Academies of Sciences TRB, aimed to enhance operational resilience in U.S. transportation agencies facing increasing environmental challenges. The primary study objective was to assess current resilience integration, identify gaps, and provide actionable recommendations. Key contributions included developing a comprehensive database of resiliency resources and creating an Operational Resiliency Online Toolkit with a resource explorer and self-assessment tool. The project culminated in a WordPress-based website that enables agencies to query resources and evaluate their operational resilience status, guiding improvements in planning and programming.}
    \resumeItemListEnd
    
    \resumeProjectHeading
    {\textbf{\href{https://artsfreightplan.com/}{ARTS Regional Freight Plan, GA \& SC}} $|$ \emph{Metro Analytics}}{2024}
    \resumeItemListStart
        \resumeItem{The Augusta Regional Transportation Study (ARTS) Regional Freight Plan update was developed to address evolving freight logistics and anticipate future trends. The project involved comprehensive existing conditions and needs analyses and coordination with stakeholders. I contributed to internal project management, including alignment across planning, GIS, public engagement, quality control teams, client communications, and meeting coordination. My involvement also supported the creation of a work program that will guide the future Metropolitan Transportation Plan for the region.}
    \resumeItemListEnd
    
    \resumeProjectHeading
    {\textbf{DARTS 2050 Metropolitan Transportation Plan Update, GA} $|$ \emph{Metro Analytics}}{2024}
    \resumeItemListStart
        \resumeItem{The Dougherty Area Regional Transportation Study (DARTS) 2050 Metropolitan Transportation Plan update aimed to create a comprehensive transportation strategy for the region through 2050.  was tasked with preparing GIS maps for the final report, managing data, and developing a work program based on project recommendations and revenue projections. To achieve this, I meticulously organized data, created clear GIS maps, and applied best practices to prioritize projects aligned with regional goals and objectives. I also developed fiscally constrained and unconstrained work programs using Federal, state, and local revenue projections. The resulting work program was tailored to the region’s needs, allowing seamless integration into the MPO’s Transportation Improvement Program (TIP).}
    \resumeItemListEnd
    
    \resumeProjectHeading
    {\textbf{Albany-DARTS Resiliency Plan, GA} $|$ \emph{Metro Analytics}}{2024}
    \resumeItemListStart
        \resumeItem{Assisted in developing a regional resiliency plan for the Albany region in Georgia, historically impacted by severe disasters such as floods and hurricanes. Conducted geospatial analysis by collecting and analyzing data on historical disruption events (e.g., FEMA 100-year floodplains, storm-damaged areas), and identified vulnerable community and transportation assets. This analysis provided an assessment of critical areas of exposure and helped guide recommendations to reduce vulnerabilities within the transportation system, enhancing the region's ability to mitigate future disruption events.}
    \resumeItemListEnd
                
    \resumeProjectHeading
    {\textbf{Missouri DOT STIP 2024-2027 \& STIP 2025-2028, MO} $|$ \emph{Metro Analytics}}{2023 \& 2024}
    \resumeItemListStart
        \resumeItem{Analyzed the societal benefits of bridge and pavement preservation investments in Missouri's 2024-2028 and 2025-2029 Statewide Transportation Improvement Programs (STIPs). Utilized the USDOT’s Benefit-Cost Analysis Guidance, leveraging Highway Performance Monitoring System (HPMS) and National Bridge Inventory (NBI) data to assess the benefits of these investments. Delivered a technical memorandum to MoDOT outlining the preservation benefits and updated the annual tracker of the benefit-cost ratios for the STIP, helping to quantify the value of MoDOT's planned infrastructure improvements.}
    \resumeItemListEnd
    
    \resumeProjectHeading
    {\textbf{Economic Impact Analysis of Utah Transit Authority, UT} $|$ \emph{Metro Analytics}}{2023-2024}
    \resumeItemListStart
        \resumeItem{Conducted an analysis of the societal benefits and broader economic impacts of Utah Transit Authority's (UTA) services, including rail, bus, and paratransit. Using the regional travel demand model, evaluated transit's impact under various scenarios as part of Utah’s Unified Plan. Additionally, employed the IMPLAN economic model to estimate economic impacts such as increased employment, household income, and fiscal benefits. The analysis demonstrated that UTA’s transit services not only benefit riders but also provide region-wide advantages through congestion relief, reduced travel costs, and improved travel times.}
    \resumeItemListEnd
    
    \resumeProjectHeading
    {\textbf{\href{https://www.stonecrestga.gov/MajorPlansAndStudies.aspx}{Stonecrest Freight Cluster Plan, GA}} $|$ \emph{Metro Analytics}}{2023-2024}
    \resumeItemListStart
        \resumeItem{Supported the development of a Freight Cluster Plan for the City of Stonecrest in coordination with the Atlanta Regional Commission (ARC) to address the transportation needs of a key freight area. Analyzed existing transportation infrastructure and traffic data to assess current conditions, collaborated with community stakeholders to identify needs, and reviewed industry trends to forecast future freight growth. Developed a work program recommending short- and long-term projects that balance future freight demands with community well-being and financial capacity, enabling sustainable economic growth while minimizing negative impacts on the local infrastructure.}
    \resumeItemListEnd
    
    \resumeProjectHeading
    {\textbf{Economic Benefit and Impacts of Utah’s Unified Plan 2023-2050, UT} $|$ \emph{Metro Analytics}}{2023}
    \resumeItemListStart
        \resumeItem{Analyzed the societal benefits and economic impacts of Utah's Unified Plan 2023-2050, developed by Wasatch Front Regional Council (WFRC) and partners. Assessed transportation investments under constrained and unconstrained funding scenarios using travel demand model outputs and USDOT guidance. Employed the IMPLAN economic model to project impacts on income growth, employment, business output, and government fiscal gains. Delivered a comprehensive report outlining the categorized societal benefits and economic impacts of these investments, providing WFRC and regional stakeholders with insights to prioritize future transportation funding and demonstrate the long-term value of these investments.}
    \resumeItemListEnd
    
    \resumeProjectHeading
    {\textbf{Ohio DOT Cleveland CCG3A Intersection, OH} $|$ \emph{Metro Analytics}}{2023}
    \resumeItemListStart
        \resumeItem {Conducted a Benefit-Cost Analysis (BCA) for Ohio DOT's Cleveland Innerbelt Modernization Plan, focusing on the Center Interchange reconstruction (Phase 3A) to improve safety and reduce congestion. Analyzed the societal costs of "build" versus "no-build" scenarios using outputs from the Northeast Ohio Areawide Coordinating Agency’s travel demand model and followed USDOT’s BCA guidance. Delivered a detailed Microsoft Excel model and a technical memorandum outlining the methodology and results, which supported Ohio DOT and NOACA in securing federal grant funding by demonstrating the project's long-term societal benefits.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{\href{https://bhandaripukar.com.np/pt-portfolio/downtown-slc-parking-study/}{Downtown Salt Lake City Parking Study}} $|$ \emph{University of Utah (MCMP Professional Project)}}{2023}
    \resumeItemListStart
        \resumeItem{A parking study for Downtown Salt Lake City was conducted as part of a professional project for the Master’s in City \& Metropolitan Planning at the University of Utah, in collaboration with Wasatch Front Regional Council (WFRC). The project involved reviewing the utilization of off-street parking within the Free Fare Zone using satellite imagery, site visits, and temporal data collection at multiple times of the day. The analysis of spatial and temporal parking occupancy informed recommendations for parking demand management policies. The study provided actionable strategies for parking demand, supply, and management, and was recognized as the "Best Professional Project of the Year" by the Department of City \& Metropolitan Planning.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{\href{https://bhandaripukar.com.np/pt-portfolio/travel-demand-modeling/}{Four-Step Travel Demand Modeling}} $|$ \emph{University of Utah}}{2023}
    \resumeItemListStart
        \resumeItem{A project on Four-Step Travel Demand Modeling was completed as part of the CVEEN 6560 - Transportation Planning course at the University of Utah. The objective was to understand the process of travel demand modeling using TransCAD and R. The project involved applying the travel demand model theory to a sample from the Utah Household Survey and other publicly available data, completing all four steps: generation, distribution, mode choice, and assignment. The result was a comprehensive documentation of the modeling process and analysis findings.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{\href{https://bhandaripukar.com.np/pt-portfolio/salt-lake-city-surface-parking-occupancy-analysis/}{Salt Lake City Surface Parking Occupancy Analysis}} $|$ \emph{University of Utah}}{2023}
    \resumeItemListStart
        \resumeItem{This project served as the final assignment for the CVEEN 6115 - Data Science for Civil Engineering course at the University of Utah. The task involved employing machine learning algorithms to automate the counting of surface parking occupancy in Downtown Salt Lake City. Using Python and the scikit-learn library, a model was developed to detect vehicles from publicly available satellite imagery data for training and testing purposes. The resulting model utilized Support Vector Machines (SVM) and Principal Component Analysis (PCA) algorithms, achieving a parking occupancy counting accuracy of 75\%.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{\href{https://bhandaripukar.com.np/pt-portfolio/traffic-impact-study-at-2100s-2100e/}{Traffic Impact Study at 2100S/2100E}} $|$ \emph{University of Utah}}{2023}
    \resumeItemListStart
        \resumeItem{For the Traffic Impact Study at the 2100S/2100E intersection in Salt Lake City, the assignment focused on analyzing the impact of a new mixed-use development on local traffic. I was tasked with using Synchro/SimTraffic to propose upgrades to the intersection. To achieve this, I collected traffic data from UDOT sources, applied trip generation methodologies, and utilized both stochastic and deterministic modeling to evaluate traffic patterns with and without the proposed development. The resulting report detailed existing traffic conditions, modeled future scenarios, and recommended intersection improvements to mitigate the development’s impact.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{\href{https://bhandaripukar.com.np/pt-portfolio/pedestrian-and-bicycle-safety-analysis/}{Built Environment Determinants of Walking and Biking Safety}} $|$ \emph{University of Utah}}{2022}
    \resumeItemListStart
        \resumeItem{Collaborated with UDOT and local partners to analyze built environment factors affecting pedestrian and bicycle crash severity for a Transportation Data Analytics workshop. Conducted geospatial analysis in R on UDOT crash data (2017-2021) to examine the impact of variables like speed limits, transit stops, intersection safety, and bicycle level-of-stress (LOS) on crash outcomes. The study found pedestrian crashes were more risk-driven, while cyclist crashes were more exposure-driven, with speed being a common risk factor. The findings recommended integrating risk and exposure assessments into policy and emphasized the importance of traffic calming measures for enhancing safety.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{\href{https://www.arcgis.com/apps/MapJournal/index.html?appid=5c94536e1840429bbd5f0e56118b9858}{Evaluation of Social Equity of Transit Accessibility in Salt Lake County, UT}} $|$ \emph{University of Utah}}{2022}
    \resumeItemListStart
        \resumeItem{As part of Advanced GIS coursework, conducted a geospatial analysis to evaluate the relationship between social equity and transit accessibility at the census tract level in Salt Lake County, UT. Measured transit accessibility using proximity to transit stations and analyzed social equity variables—such as minority populations, renter-occupied households, and households without vehicles—using demographic data. Applied spatial autoregressive models to explore the connection between transit access and equity. The study revealed that social equity variables are significantly higher for areas within a 20-minute walking distance of TRAX lines, benefiting residents in these transit-adjacent neighborhoods.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{\href{https://bhandaripukar.com.np/pt-portfolio/thriving-in-place-at-liberty-wells/}{Thriving in Place: Salt Lake City, UT}} $|$ \emph{University of Utah}}{2022}
    \resumeItemListStart
        \resumeItem{Contributed to Salt Lake City's "\href{https://thrivinginplaceslc.org/}{Thriving in Place}" initiative, which aims to identify neighborhoods vulnerable to resident displacement and develop anti-displacement strategies. Focused on the Liberty Wells neighborhood, data was collected through resident surveys to assess changes in housing affordability and its impacts over time. Conducted statistical and empirical analyses to identify actionable policies that preserve, protect, and increase housing availability. Proposed strategies to help residents stay and thrive amid city growth, contributing to a broader understanding of gentrification and displacement in Salt Lake City.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{\href{https://bhandaripukar.com.np/pt-portfolio/a-15-minute-salt-lake-city/}{15-Minute Salt Lake City: Pedestrian Accessibility Analysis, UT}} $|$ \emph{University of Utah}}{2022}
    \resumeItemListStart
        \resumeItem{Conducted an analysis of pedestrian accessibility in Salt Lake County as part of CMP 6720 – Land Use \& Transportation Planning coursework. The study evaluated how well different areas of the county align with the principles of a 15-minute city. Applied buffer analysis on geospatial data of public amenities (schools, health centers, groceries, parks, etc.), using a distance decay function to measure accessibility and the Analytical Hierarchical Process to weigh the importance of each amenity. The analysis found that high pedestrian accessibility is concentrated in Salt Lake City's downtown and Sugarhouse areas, with some outlying pockets of accessibility in places like Murray and Draper, though these are exceptions.}
    \resumeItemListEnd
    
    \resumeProjectHeading
    {\textbf{\href{https://bhandaripukar.com.np/pt-portfolio/greywater-recycling-at-west-village-redevelopment/}{Greywater Recycling at West Village Redevelopment at University of Utah}} $|$ \emph{University of Utah}}{2021}
    \resumeItemListStart
        \resumeItem{Conducted as part of the CMP 6610 - Urban Ecology coursework, developed a conceptual plan to enhance sustainability at the University of Utah through greywater recycling. Analyzed water usage data and reviewed literature on greywater production to identify strategies for reducing water usage and recycling greywater, particularly for landscaping. Proposed the integration of a greywater recycling facility within the West Village Student Housing redevelopment, alongside mixed recycling facilities for storing the recycled water. This cost-effective strategy aims to significantly reduce the university's water footprint and should be considered for future policy and project prioritization.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{\href{https://bhandaripukar.com.np/pt-portfolio/suitability-of-bicycle-sharing-station-in-university-of-utah-campus/}{Suitability Analysis of Bicycle Sharing Station in University of Utah}} $|$ \emph{University of Utah}}{2021}
    \resumeItemListStart
        \resumeItem{Conducted as part of CMP 6700 - Walk \& Bike Planning/Design, this project aimed to support the University of Utah's sustainability initiatives by identifying optimal locations for bicycle sharing stations on campus. The study focused on selecting appropriate factors, variables, and criteria from literature reviews to inform the siting process. Utilizing the Analytical Hierarchy Process (AHP), raster images of the identified variables were overlaid to pinpoint potential station locations. The research recommended establishing micro-mobility stations at thirteen identified sites, while suggesting that the fleet size for bike-sharing should be determined through further analysis of user demand across the campus.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{\href{https://bhandaripukar.com.np/pt-portfolio/salt-lake-city-profile-2010-2019/}{Salt Lake City Profile 2010-2019, UT}} $|$ \emph{University of Utah}}{2021}
    \resumeItemListStart
        \resumeItem{Developed a comprehensive city profile of Salt Lake City as part of the CMP 6010 – Community and Regional Analysis coursework. Conducted advanced analysis of demographic, economic, housing, and transportation data from primary sources such as the US Census Bureau to assess the city's historical and current conditions for the periods between 2010 and 2019. Projected future trends based on these analyses and complemented the findings with literature reviews and local knowledge. The resulting report offers a detailed overview of Salt Lake City's evolving needs and conditions, providing valuable insights for future city planning and development programs.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{\href{https://storymaps.arcgis.com/stories/ed6db42d441e4b7b864d7969fac4ba3a}{Wasatch Hollow: Mapping the story of a changing neighborhood, UT}} $|$ \emph{University of Utah}}{2021}
    \resumeItemListStart
        \resumeItem{Conducted as part of CMP 6430 - Community Engagement in Planning, this project focused on documenting the changing conditions in the Wasatch Hollow neighborhood of Salt Lake City, particularly regarding housing unaffordability and displacement. The research involved reviewing historical records, analyzing secondary data, and conducting public interviews and surveys to gather firsthand experiences from residents. The findings were compiled into an ArcGIS StoryMap, which visually narrates the neighborhood's history, current conditions, and transformations in community assets while capturing recurring themes in the stories shared by residents.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{\href{https://www.arcgis.com/apps/MapSeries/index.html?appid=a89311d3ac89482484c5cd421781f2ac}{Folsom Trail Extension along 400W in Salt Lake City, UT}} $|$ \emph{University of Utah}}{2021}
    \resumeItemListStart
        \resumeItem{As part of the CMP 6700 - Walk \& Bike Planning/Design coursework, developed a design for a 1,000 ft extension of the Folsom Trail along 400W, northwest of downtown Salt Lake City. The plan accommodated both bicycle and pedestrian users, with a focus on improving safety at two key intersections, particularly near West High School due to high student traffic. The design prioritized safety, accessibility, and enhanced multimodal experiences for trail users. The final submission included 2D and 3D visualizations (using Adobe Illustrator and SketchUp) and a 3D animation showcasing the proposed improvements.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{\href{https://bhandaripukar.com.np/pt-portfolio/study-on-landcover-change-and-risk-analysis-of-west-kathmandu-valley/}{Landcover Change and Risk Analysis of West Kathmandu Valley}} $|$ \emph{Tribhuvan University}}{2021}
    \resumeItemListStart
        \resumeItem{A landcover change and risk analysis was conducted for West Kathmandu Valley as part of the "Geospatial Technologies for Urban Planning" course at Tribhuvan University. The project involved calculating descriptive statistics of spatio-temporal landcover changes using UNDP data and developing an integrated disaster risk map. An Analytical Hierarchical Process (AHP) was applied for hazard and socio-economic vulnerability analysis in GIS. The final analysis identified trends in landcover changes and highlighted high-risk areas, providing valuable insights for stakeholders to design spatially targeted policies for resilient and sustainable urban growth.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Masterplan of Padma Kanya Multiple Campus} $|$ \emph{IOE, Research Training and Consultancy Services}}{2020}
    \resumeItemListStart
        \resumeItem{Developed a comprehensive masterplan for Padma Kanya Multiple Campus, one of Nepal’s oldest women’s colleges, to address years of underdevelopment and prepare for future growth needs. The project involved reviewing the campus's strategic plan, conducting site investigations, and revising the space program to accommodate expansion. Architectural designs, digital models, and visualizations were created to communicate the redevelopment plan to stakeholders. Additionally, potential funding sources were identified to support future implementation. The final master plan provided a strategic framework for modernizing the campus and meeting future infrastructure demands.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Conservation and Development Work of Pashupatinath Temple Complex} $|$ \emph{Archetype Design Consult}}{2020}
    \resumeItemListStart
        \resumeItem{Pashupatinath Temple, a UNESCO World Heritage Site and one of the holiest Hindu temples, required a preservation and reconstruction plan following the damage from the 2015 Gorkha earthquake. Leading a team of architects, I conducted an assessment of nearly 30 monuments within the heritage zone and proposed conservation interventions aligned with best practices. Additionally, a master plan for redeveloping the Bagmati River ghat as a religious, cultural, and community space was developed in an effort to revitalize the entire monument area. The masterplan was successfully implemented by the Pashupati Area Development Trust, revitalizing the damaged monuments and enhancing the Guheswori Ghat area as a public space.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{\href{https://bhandaripukar.com.np/sindhuligadhi-a-living-war-memorial/}{Conservation Masterplan of Singhuligadhi Area}} $|$ \emph{Archetype Design Consult}}{2019}
    \resumeItemListStart
        \resumeItem{Singhuligadhi, a historic hill fort central to Nepal's resistance against British forces in the 1800s, was slated for redevelopment as a war memorial. The task involved documenting the fort’s existing conditions, proposing conservation interventions, and designing a memorial park to attract historical tourism. The design team, led by me, documented the site, referenced historical records, and developed a strategy aligned with UNESCO and ICOMOS standards. The master plan was presented to the Department of Archaeology and local government, and the site is now redeveloped as a war memorial and museum following the plan.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{\href{https://bhandaripukar.com.np/pt-portfolio/earthquake-memorial-at-barpak/}{Earthquake Memorial at Barpak, Gorkha}} $|$ \emph{Tribhuvan University (B.Arch Thesis)}}{2018}
    \resumeItemListStart
        \resumeItem{Three years after the 2015 Gorkha earthquake, the Barpak community, the earthquake's epicenter, was undergoing redevelopment. In response, the Government of Nepal initiated plans for an Earthquake Memorial to honor those affected, drive tourism, and revitalize the community. The task involved designing a memorial that not only commemorated lives lost but also symbolized resilience and served as a community refuge in future disasters. Extensive research on architectural elements of memory and experience, including form, materials, and lighting, was conducted to inform the design. The final design was submitted as the B.Arch thesis and earned the Best Architecture Thesis of the Year award from Asian Paints and the Department of Architecture.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{\href{https://bhandaripukar.com.np/pt-portfolio/nuwakot-durbar-conservation/}{Conservation of Nuwakot Durbar Area}} $|$ \emph{Tribhuvan University}}{2017}
    \resumeItemListStart
        \resumeItem{The historic Nuwakot Durbar area, a key site in Nepal's unification and listed on UNESCO's tentative World Heritage Site list, was facing deterioration due to neglect and unplanned development. A conservation masterplan was developed to document existing monuments and create a framework for sustainable development that met contemporary community needs while preserving the heritage site’s historical significance. The project involved documenting key historic structures through architectural drawings in line with ICOMOS and UNESCO standards, drafting preservation bylaws, and creating visual materials to engage the community in the conservation process. The final documentation and bylaws were presented to the local community and submitted to the Nuwakot Area Development Authority and the Department of Archeology to support ongoing preservation efforts.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{\href{https://bhandaripukar.com.np/pt-portfolio/barpak-resettlement-plan-ward-4/}{Barpak Resettlement Plan: Ward 4}} $|$ \emph{Tribhuvan University}}{2017}
    \resumeItemListStart
        \resumeItem{In response to the 2015 Gorkha earthquake, which demolished nearly 90\% of Barpak village, a conceptual masterplan was developed to aid in the reconstruction of a section of the village with a focus on resilience. The plan emphasized community connectivity, access to essential amenities, and the preservation of local architecture through four housing prototypes that integrated traditional construction methods with modern, earthquake-resistant techniques. The master plan and prototypes were presented to the local government to support their resettlement and rebuilding efforts.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{\href{https://bhandaripukar.com.np/pt-portfolio/cafeteria-at-ioe-pulchowk-campus/}{Cafeteria at IOE, Pulchowk Campus}} $|$ \emph{Asian Paints National Design Competition}}{2017}
    \resumeItemListStart
        \resumeItem{For a national architectural design competition organized by Asian Paints, a conceptual cafeteria design was created for the IOE, Pulchowk Campus, near the Department of Architecture. The design featured an elevated structure utilizing wood and metal components, ensuring the preservation of existing trees by incorporating them into the layout. This design achieved runner-up status at the college level and qualified for the national competition.}
    \resumeItemListEnd

\resumeSubHeadingListEnd